Design and Implementation of Probabilistic Programming Language Anglican

### 2016-11-21 paper/paper.tex
missing and drawn
performance comparison citations, some small edits

Anglican language syntax, compilation, invocation, and runtime
support of Anglican queries are discussed in detail in further
sections.

\section{Design Outline}

@@

\hy{I found this section confusing in the following sense. First,
it does not highlight the most interesting aspects of the compilation
of Anglican. It gives a good overview on how the compilation is
implemented, but a reader might want to see something unique and
interesting about Anglican. To me, the most interesting part of the
compilation is the treatment of probabilistic constructs in Anglican's
CPS transformation. How are sample,
observe and stochastic memoization compiled? How should the standard
CPS transformation be modified in order to handle these constructs?
The use of state can be one answer for the second question.
The second most interesting part is about the use of trampolining
the mix with Clojure code.
Second, the section assumes that a reader is already familiar 
with Clojure or something specific to probabilistic programming. For 
instance, it might be that a reader  has never heard about
Clojure records and stochastic memoization. Then, she or he
would have difficulties in following this section. 
What should we do? One option is not to do anything. Another is
to take care of the second point. That is, we make the section
easily followed by someone who does not know Clojure. The third
is to restructure the section and to take care of my first criticism.}

\dt{I believe I partially addressed the above comment, but need to
think more about it.}

@@

\hy{This subsection is also not quite self-contained. Someone
who is not familiar with Clojure or Anglican codebase is likely
to get lost. On the other hand, it is a good overview or guide
for those who want to study the implementation of Anglican. One
way to address this presentation issue while keeping the benefits
of the current text is to include some extended examples. For instance,
in the beginning of the paper, we might include several
Anglican examples. Then, we show that how these examples get
cps-transformed. Next, we present the implementation of inference
algorithms in Anglican using semi pseudo code; this is not quite
an implementation in Clojure but gives a good sketch on how
various functions are implemented in each inference algorithm.
Finally, we show how these algorithms work on cps-transformed 
examples.}

@@

\begin{center}
\begin{tabular}{l l}
    \textbf{old} & \textbf{new} \\ \hline
    {}\texttt{[C1 0]} & \texttt{[C1 0]} \\
    {}\texttt{[C2 0]} & \texttt{[C2 0]} \\
    {}\texttt{[C2 1]} & \textit{unused} \\
    {}\texttt{[C1 16]} & \texttt{[C1 16]} \\
    {}\texttt{[C1 17]} & \texttt{[C1 17]} \\
    {}\texttt{[C1 18]} & \textit{unused} \\
    {}\texttt{[C2 16]} & \texttt{[C2 16]} \\
    \textit{redrawn} & \texttt{[C2 17]} \\
    {}\texttt{[C3 0]} & \texttt{[C3 0]}
\end{tabular}
\end{center}

@@

Implementing a probabilistic language on top and in tight
integration with a functional language, Clojure, both helped
us to accomplish an ambitious goal in a short time span, and
provided important insights on structure and semantics of
probabilistic concepts incorporated in Anglican. Efficiency
and expressive power of Anglican owe to adherence to the
functional approach as much as to rich inference opportunities
of the Anglican environment.

>>>>

Comparisons of Anglican with other implementations of
probabilistic programming languages~\cite{SGG15}\cite[pp.
32--33]{P16} demonstrate that Anglican achieves state-of-the-art
computational efficiency without sacrificing expressiveness.
Anglican language syntax, compilation, invocation, and runtime
support of Anglican queries are discussed in detail in further
sections.
\section{Design Outline}

@@

@@

@@

\begin{tabular}{l l}
    \textbf{old} & \textbf{new} \\ \hline
    {}\texttt{[C1 0]} & \texttt{[C1 0]} \\
    {}\texttt{[C2 0]} & \texttt{[C2 0]} \\
    {}\texttt{[C2 1]} & \textit{unused} \\
    {}\texttt{[C1 16]} & \texttt{[C1 16]} \\
    {}\texttt{[C1 17]} & \texttt{[C1 17]} \\
    {}\texttt{[C1 18]} & \textit{unused} \\
    {}\texttt{[C2 16]} & \texttt{[C2 16]} \\
    \textit{missing} & \texttt{[C2 17]} \textit{drawn}\\
    {}\texttt{[C3 0]} & \texttt{[C3 0]}
\end{tabular}

@@

Implementing a probabilistic language on top and in tight
integration with a functional language, Clojure, both helped
us to accomplish an ambitious goal in a short time span, and
provided important insights on structure and semantics of
probabilistic concepts incorporated in Anglican. Computational
efficiency and expressive power of Anglican owe to adherence to
the functional approach as much as to rich inference
opportunities of the Anglican environment.
